Stability

### 2022-09-29 Rmd/Stability.Rmd
edit plots

Relationship between richness-synchrony with different synchrony indice.

A- Total richness ~ log VR

@@

#plot
plots_rich <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=log_VR, y=S_total) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "log VR",y="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

@@

rich<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

\newpage
B- total richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich2<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

#goodness of fit measures
rich2_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

C- mean richness ~ log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich3_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.3 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.3$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

D- mean richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich4<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich4_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.4 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.4$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.4$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.4$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

p7=sta_polli_Smean_plot4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

>>>>

Relationship between synchrony ~ richness with different synchrony indice.

A- log VR ~ Total richness

@@

#plot
plots_rich <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=S_total, y=log_VR) + 
 theme_bw()+ geom_point(size = 5) + labs(y = "log VR",x="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

@@

rich<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(log_VR~S_total,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(log_VR~S_total,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(log_VR~S_total,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.1$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.1$plots[[4]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "H.calycinum")+scale_x_continuous(limits = c(4, 7))+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.1$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_total, y = log_VR),shape=20)+ 
  labs(x = "total_richness",y="log_VR",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

\newpage
B- Loreau & Mazancourt syncrony index ~ total richness

#plot
plots_rich2 <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=S_total, y=syncLM) + 
 theme_bw()+ geom_point(size = 5) + labs(x="Total richness",y = "syncLM")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_rich2[[1]],plots_rich2[[2]],plots_rich2[[3]],plots_rich2[[4]],plots_rich2[[5]],plots_rich2[[6]],plots_rich2[[7]], ncol=3, nrow=3)

rich2<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(syncLM ~S_total,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

#goodness of fit measures
rich2_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(syncLM ~S_total,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(syncLM ~S_total,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "H.calycinum") + scale_x_continuous(limits = c(4, 7)) +  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  S_total, y = syncLM),shape=20)+ 
  labs(y = "syncLM",x="total richness",subtitle = "L.stoechas")+ scale_x_continuous(limits = c(5, 13))+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

C- log VR ~ mean richness

#plot
plots_rich3 <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes( x=S_mean, y=log_VR) + 
 theme_bw()+ geom_point(size = 5) + labs(y = "log_VR",x="mean richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_rich3[[1]],plots_rich3[[2]],plots_rich3[[3]],plots_rich3[[4]],plots_rich3[[5]],plots_rich3[[6]],plots_rich3[[7]], ncol=3, nrow=3)

rich3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(log_VR ~ S_mean,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich3_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(log_VR ~ S_mean,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.3 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(log_VR ~ S_mean,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.3$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(y = "log_VR",x="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer") + scale_x_continuous(limits = c(4, 11)) +  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+ scale_x_continuous(limits = c(3, 12))+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+ scale_x_continuous(limits = c(2, 5.5))+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.3$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_mean, y = log_VR),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

D- Loreau & Mazancourt syncrony index ~  mean richness

#plot
plots_rich4 <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes( x=S_mean, y=syncLM) + 
 theme_bw()+ geom_point(size = 5) + labs(y = "syncLM",x="mean richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_rich4[[1]],plots_rich4[[2]],plots_rich4[[3]],plots_rich4[[4]],plots_rich4[[5]],plots_rich4[[6]],plots_rich4[[7]], ncol=3, nrow=3)

rich4<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(syncLM ~ S_mean,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich4_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(syncLM ~ S_mean,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.4 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(syncLM ~ S_mean,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.4$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.4$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.4$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.4$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_mean, y = syncLM),shape=20)+ 
  labs(x = "S_mean",y="syncLM",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

p7=sta_polli_Smean_plot4$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
